---
title: "lazappi"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{lazappi}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(lazappi)
```

Introduction
============

This vignette provides brief introduction to the functions in my package.

Cats
====

Do I love cats?

```{r cats}
cat_function()
```

What if I don't?

```{r no-cats}
cat_function(FALSE)
```

Scaling
=======

Scale min-max
-------------

The `scale_minmax()` function scales values between zero and one.

```{r scale-minmax}
scale_minmax(c(0:10))
scale_minmax(c(-10:10))
```

Scale mean
----------

The `scale_mean()` function performs mean scaling
(see https://en.wikipedia.org/wiki/Feature_scaling#Mean_normalization).

```{r scale-mean}
scale_mean(c(0, 1))
scale_mean(c(-1, 1))
```

Scale unit
----------

The `scale_unit()` function performs unit length scaling
(see https://en.wikipedia.org/wiki/Feature_scaling#Scaling_to_unit_length).

```{r scale-unit}
scale_unit(c(0, 1))
scale_unit(c(-1, 1))
```

Names
=====

Name seq
--------

Sometimes it is useful to give a sequential set of names to a vector (or
vector-like object). The `name_seq()` function is an easy way to do this.

```{r name-seq}
name_seq(1:3)
```

If there already some names present these are kept.

```{r name-seq-keep}
name_seq(c(1, B = 2, 3))
```

You can also provide a prefix for the new names.

```{r name-seq-prefix}
name_seq(1:3, prefix = "Item")
```

Sets
====

These are some useful functions for working with lists of sets.

Intersect list
--------------

The `intersect_list()` function provides the intersection off all vectors in a
list.

```{r intersect-set}
sets <- list(1:3, 2:4, 3:5)
intersect_list(sets)
```

Union list
----------

The `union_list()` function provides the union off all vectors in a list.

```{r union-set}
union_list(sets)
```


Setdiff lists
-------------

The `setdiff_lists()` function finds all items that are present in the
intersection of one list of vectors but not present in the union of another list
of vectors.

```{r setdiff-lists}
setdiff_lists(list(c(1:3), c(2:4)), list(c(1, 2)))
```

Venn sets
---------

The `venn_sets()` function takes a list of vectors and returns the sets of items
corresponding to each region in a Venn diagram.

```{r venn-sets}
venn_sets(sets)
```

Combine sets
------------

The `combine_sets()` function finds all combinations of a list of vectors using
either the union or the intersect.

```{r combine-sets}
combine_sets(sets, method = "union")
combine_sets(sets, method = "intersect")
```

All combos
----------

The `all_combos()` function takes a vector and returns all combinations of the
items (of a set length).

```{r all-combos}
all_combos(1:4)
all_combos(1:4, min = 2, max = 3)
```


